Fuzzy Extractors for Noisy Sources with More Errors Than Entropy

### 2015-02-06 trunk/constantRate/ConstCompFuzzExt-crypto.tex
happy with intro and obfuscation references

\paragraph{Our Contributions: Handling More Errors than Entropy}
We provide the first constructions of fuzzy extractors that can be used for large classes of sources that have more errors than entropy.  Our constructions work for Hamming errors for strings $w$ of length $\gamma$ over some alphabet $\mathcal{Z}$. Naturally, as argued above, these constructions cannot work for all sources of a given entropy; instead, each construction takes advantage of the specific properties of a source.

Our first construction works for \emph{sources with high-entropy samples}: these are sources for which a randomly sampled substring of some superlogarithmic length is likely to have superlogarithmic  entropy. For example, a source can satisfy this condition if a constant fraction of symbols are almost $k$-wise independent for some superlogarithmic $k$ (note there is no total entropy requirement:  the total entropy of such a source may be not  much greater than the entropy of the sample). This construction uses digital lockers~\cite{canetti2008obfuscating}, which lock up the output $r$ using the sampled substring as the key to the locker. Such lockers can be constructed using a salted hash function under appropriate assumptions or, more generally, from point obfuscation, as we discuss below.

@@

\paragraph{Relation to Obfuscation} 
Our constructions use simulation-secure obfuscation of digital lockers, which can be achieved by simple efficient constructions using a salted hash function or modular exponentiation under appropriate assumptions~\lnote{refs needed? especially for salted hash?}\bnote{the canetti 98 paper is okay for one time but we need reusability, the mod exp is bitanski canetti }
The precise definition we require is not full-fledged virtual black-box obfuscation~\cite{barak2001possibility}. Instead, we rely on the relaxed notion of \emph{virtual grey-box} obfuscation, as long as it remains secure even when several digital lockers with correlated keys are composed~\cite{bitansky2010strong}.

@@

\paragraph{Open Problems}
\lnote{can we kill this paragraph? I don't see how it helps our cause. And in any case the grouping construction supports constant size alphabets}
All of our constructions support more errors than entropy by using two metrics spaces.  Errors are tolerated in one metric space and corrected in a second.  To handle more errors than entropy,  we map to a metric space where multiple error patterns are grouped together.  All our constructions require the first metric space to have a super-constant size alphabet.  An alternative approach to the problem may support constant size alphabets.

@@

In this work we restrict the distribution of the original reading $w$ and allow $w'$ to be an arbitrary point within distance $t$.  An alternative approach is to restrict the set of $w'$ where $\gen$ produces the correct key.%  A meaningful restriction of correctable errors is an open problem.

@@

In this section, we give a formal definition of the required notion of obfuscation.
We require that the obfuscation is composable and secure with respect to auxiliary input. Composable auxiliary-input VGB obfuscators for point functions and digital lockers are constructed in \cite[Theorem 6.1]{bitansky2010strong} from the Strong Vector Decision Diffie-Hellman assumption, which is a generalization of the strong DDH assumption of \cite{canetti1997towards} for tuples of points. They can also be constructed by assuming strong properties of cryptographic hash functions~\cite{canetti1997towards}.

>>>>

\paragraph{Our Contributions: Handling More Errors than Entropy}
We provide the first constructions of fuzzy extractors that can be used for large classes of sources that have more errors than entropy.  Our constructions work for Hamming errors for strings $w$ of length $\gamma$ over some alphabet $\mathcal{Z}$. Naturally, as argued above, these constructions cannot work for all sources of a given entropy and for any $t$ errors. In this work, each construction takes advantage of the specific properties of a source, but still works for any $t$ errors. (It is an open problem to achieve our goal by restricting the error patterns instead of restricting the source distribution.)

Our first construction works for \emph{sources with high-entropy samples}: these are sources for which a randomly sampled substring of some superlogarithmic length is likely to have superlogarithmic  entropy. For example, a source can satisfy this condition if a constant fraction of symbols are almost $k$-wise independent for some superlogarithmic $k$ (note there is no total entropy requirement:  the total entropy of such a source may be not  much greater than the entropy of the sample). This construction uses digital lockers~\cite{canetti2008obfuscating}, which lock up the output $r$ using the sampled substring as the key to the locker. Such lockers can be constructed very efficiently via a single application of a cryptographic hash function (under appropriate assumptions) or, more generally, from point obfuscation, as we discuss below.

@@

\paragraph{Relation to Obfuscation} 
Our constructions use simulation-secure obfuscation of digital lockers. The precise definition we require is not full-fledged virtual black-box obfuscation~\cite{barak2001possibility}. Instead, we rely on the relaxed notion of \emph{virtual grey-box} obfuscation, as long as it remains secure even when several digital lockers with correlated keys are composed~\cite{bitansky2010strong}.

The following simple and efficient construction of digital lockers, proposed by Lynn, Prabhakaran, and Sahai~\cite[Section 4]{lynn2004positive}, provides the desired security in the random oracle model of~\cite{DBLP:conf/ccs/BellareR93}. Let $H$ be a cryptographic hash function, modeled as a random oracle. To lock up a value $y$ using a key $x$, output the pair $r, H(r, x)\oplus (y||0^k)$, where $r$ is a nonce, $||$ denotes concatenation, and $k$ is some security parameter. As long as the entropy of $x$ is superlogarithmic, the adversary has negligible probability of finding the correct $x$; and if the adversary doesn't find the correct $x$, then the adversarial knowledge about $x$ and $y$ is not significantly affected by this locker.  Concatenation with $0^k$ is used to make sure that it is possible to tell (with certainty $1-2^{-k}$) when the correct value is unlocked.

It is seems plausible that in the real world (without random oracles), specific cryptographic hash functions, if used in this construction, will provide the necessary security~\cite[Section 3.2]{canetti2008obfuscating}, \cite[Section 8.2.3]{dakdoukThesis}. 
Moreover, Bitansky and Canetti~\cite{bitansky2010strong}, building on the work of~\cite{canetti2008obfuscating,CKVW10}, show how to obtain composable digital lockers based on a strong version of the Decisional Diffie-Hellman assumption without random oracles.

@@

%\paragraph{Open Problems}
%\lnote{can we kill this paragraph? I don't see how it helps our cause. And in any case the grouping construction supports constant size alphabets}
%All of our constructions support more errors than entropy by using two metrics spaces.  Errors are tolerated in one metric space and corrected in a second.  To handle more errors than entropy,  we map to a metric space where multiple error patterns are grouped together.  All our constructions require the first metric space to have a super-constant size alphabet.  An alternative approach to the problem may support constant size alphabets.

@@

%In this work we restrict the distribution of the original reading $w$ and allow $w'$ to be an arbitrary point within distance $t$.  An alternative approach is to restrict the set of $w'$ where $\gen$ produces the correct key. \lnote{move this somewhere that makes more sense, probably above where we talk about a ball around a $w'$ and the obvious impossibility}%  A meaningful restriction of correctable errors is an open problem. 
%\fi

@@

In this section, we give a formal definition of the required notion of obfuscation.
We require that the obfuscation is composable and secure with respect to auxiliary input. Composable auxiliary-input VGB obfuscators for point functions and digital lockers are constructed in \cite[Theorem 6.1]{bitansky2010strong} (following \cite{canetti2008obfuscating,CKVW10}) from the Strong Vector Decision Diffie-Hellman assumption, which is a generalization of the strong DDH assumption of \cite{canetti1997towards} for tuples of points. As described in the Introduction, they can also be constructed by assuming strong properties of cryptographic hash functions~\cite{canetti1997towards}, \cite[Section 4]{lynn2004positive}, \cite[Section 3.2]{canetti2008obfuscating}, \cite[Section 8.2.3]{dakdoukThesis}.
